---
output: github_document
---

# sequential-SDiD
Sequential Synthetic Difference-in-Differences (sequential SDiD) estimator for event studies with staggered treatment adoption.

This package estimates treatment effect, particularly when the parallel trends assumption fails.


## Installation

The package can be installed from github using devtools.
```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("AntonZudin/sequential-SDiD")
```


## Usage 
```{r, setup}
library(seq.sdid)
data(CHC)
set.seed(42)
```
The package uses 2 functions to prepare the dataset . 

### 1. `to_wide`

* Converts panel from long to wide format.
* Creates Y, W and X dataframes with adoption date column being the first one.


### 2. `prepare_wide`

* If the level is `cohort`, aggregates on the data on the cohort level.
* If the level is `unit`, removes the adoption date column. 

```{r}
panel <- to_wide(CHC,
  unit = 1, time = 3, outcome = 2,
  treatment = 4, contr_covs = c(5), treat_covs = c(),
  weights = 6
)

panel$X$popwt <- panel$X$popwt / 10000

panel_avg <- prepare_wide(panel, level = "cohort")
```

Estimate the noise variance on the untreated part of the panel.
```{r}
s2 <- estimate_s2(panel$Y[, -1], panel$W[, -1], panel$X$popwt)
```


```{r}
est <- sequential_estimator(
  panel_avg,
  s2 = s2,
  type = "both",
  aggregate_effect = aggregate_inv_did_var)
print(est, n_lags = 11)
```

Estimate standard error with Bayesian bootstrap.
```{r}
se <- vcov(est, panel, B = 1000)
cat("St. error of SDiD estimator:", "\n")
cat(sprintf("%1.2f", se$se_sdid[1:11]), "\n\n")
cat("St. error of DiD estimator:", "\n")
cat(sprintf("%1.2f", se$se_did[1:11]), "\n")
```


```{r, fig.retina=2, out.height = "100%", out.width = "100%"}
plot(
  est, se, 11,
  error_bar_width = 0.4, xlab = "Lags",
  legend_position = "right"
)
```

#### References
Dmitry Arkhangelsky, Aleksei Samkov.
<b>Sequential Synthetic Difference in Differences</b>, 2025.
[<a href="https://arxiv.org/abs/2404.00164">arxiv</a>]
