---
output: github_document
---

# sequential-SDiD
Sequential Synthetic Difference-in-Differences (sequential SDiD) estimator for event studies with staggered treatment adoption.

This package estimates average treatment effect, particularly when the parallel trends assumption fails.


## Installation

The package can be installed from github using devtools.
```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("AntonZudin/sequential-SDiD")
```


## Usage 
```{r, setup}
library(seq.sdid)
data(CHC)
```
The package uses 2 functions to prepare the dataset . 

### 1. `to_wide`

* Converts panel from long to wide format.
* Creates Y, W and X dataframes with adoption date column being the first one.


### 2. `prepare_wide`

* If the level is `cohort`, aggregates on the data on the cohort level.
* If the level is `unit`, removes the adoption date column. 

```{r}
panel <- to_wide(CHC,
  unit = 1, time = 3, outcome = 2,
  treatment = 4, contr_covs = c(5), treat_covs = c(),
  population = 6
)

panel$X$popwt <- panel$X$popwt / 10000

panel_avg <- prepare_wide(panel, level = "cohort")
```

```{r}
set.seed(42)
s2 <- estimate_s2(panel$Y[, -1], panel$W[, -1], panel$X$popwt)
est <- sequential_estimator(
  panel_avg,
  s2 = s2,
  type = "sdid")
est

se <- vcov(est, panel)
se
```


```{r, fig.retina=2}
plot(est, se)
```

