---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, setup}
library(seq.sdid)
data(CHC)
set.seed(42)
```


First, you need to convert your data from long panel to wide one to estimate the effect. 
The package uses 2 functions to prepare the dataset. 

### 1. `to_wide`
- Converts panel from long to wide format.
- Creates Y, W and X dataframes with adoption date column being the first one.
  - Y is an N x T outcome dataframe.
  - W is N x T dataframe with stair-like structure due to staggered adoption.
  - X is dataframe with auxiliary data like weights and covariates.


### 2. `prepare_wide`
- If the level is `cohort`, aggregates on the data on the cohort level.
- If the level is `unit`, removes the adoption date column.
- The Y and W dataframes are converted to matrices, X dataframe remains the same.

```{r}
panel <- to_wide(CHC,
  unit = 1, time = 3, outcome = 2,
  treatment = 4, contr_covs = c(5), treat_covs = c(),
  weight = 6
)

panel$X$popwt <- panel$X$popwt / 10000

panel_avg <- prepare_wide(panel, level = "cohort")
```

1. Estimate `s^2` - noise variance. s2 is utilized in determining the regularization parameter: $\eta^2 = s^2/n^{0.9}$. To get upper bound of `s^2`, time and unit fixed effects are estimated on the untreated observations. Then `s^2` is computed as residual sum of squares divided by the degrees of freedom. If the weights are passed, WLS is estimated rather then OLS.   
```{r}
s2 <- estimate_s2(panel$Y[, -1], panel$W[, -1], panel$X$popwt)
```

You can change default cohort weights (sum of weights of units in the cohort). 
To weight the estimated effects by the provided weights,
you need to set aggregate_by_weight function for aggregate_effect parameter. 
```{r}
panel_avg$coh_weights
```

2. Estimate the treatment effect.

You can specify your own function for `aggregate_effect` and `penalty_func` functions.
- The first function specifies how the aggregation of estimated effects will be conducted. 
  For  should take the following parameters: tau, var, W, coh_weights, N0, N.

- The second function computes regularization parameter $\eta$. If you have any prior domain knowledge on this parameter, you can create your own function for that. This function should have `s2` and `N` as arguments.  
```{r}
est <- sequential_estimator(
  panel_avg,
  s2 = s2,
  type = "both",
  aggregate_effect = aggregate_inv_did_var,
  penalty_func = default_penalty
)
print(est, n_lags = 11)
```

3. Conduct Bayesian bootstrap to obtain standard errors for the estimator. 
```{r}
se <- vcov(est, panel, B = 1000)
cat("St. error of SDiD estimator:", "\n")
cat(sprintf("%1.2f", se$se_sdid[1:11]), "\n\n")
cat("St. error of DiD estimator:", "\n")
cat(sprintf("%1.2f", se$se_did[1:11]), "\n")
```

```{r,fig.retina = 3, fig.width=9, fig.height=6, out.height = "100%", out.width = "100%"}
plot(
  est, se, 11,
  error_bar_width = 0.4, xlab = "Lags",
  legend_position = "right"
)
```
