---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Usage 
```{r, setup}
library(seq.sdid)
data(CHC)
set.seed(42)
```


First, you need to convert your data from long panel to wide one to estimate the effect. 
The package uses 2 functions to prepare the dataset. 

### 1. `to_wide`
- Converts panel from long to wide format.
- Creates Y, W and X dataframes with adoption date column being the first one.
  - Y is an N x T outcome dataframe.
  - W is N x T dataframe with stair-like structure due to staggered adoption.
  - X is dataframe with auxiliary data like weights and covariates.


### 2. `prepare_wide`
- If the level is `cohort`, aggregates on the data on the cohort level.
- If the level is `unit`, removes the adoption date column.
- The Y and W dataframes are converted to matrices, X dataframe remains the same.

```{r}
panel <- to_wide(CHC,
  unit = 1, time = 3, outcome = 2,
  treatment = 4, contr_covs = c(5), treat_covs = c(),
  population = 6
)

panel$X$popwt <- panel$X$popwt / 10000

panel_avg <- prepare_wide(panel, level = "cohort")
```

1. Estimate `s^2` - noise variance. s2 is utilized in determining the regularization parameter: $\eta^2 = s^2/n^{0.9}$. To get upper bound of `s^2`, time and unit fixed effects are estimated on the untreated observations. Then `s^2` is computed as residual sum of squares divided by the degrees of freedom. If the weights are passed, WLS is estimated rather then OLS.   
2. Estimate the average treatment effect.
3. Conduct Bayesian bootstrap to obtain standard errors for the estimator. 
```{r}
s2 <- estimate_s2(panel$Y[, -1], panel$W[, -1], panel$X$popwt)
est <- sequential_estimator(
  panel_avg,
  s2 = s2,
  type = "sdid")
est

se <- vcov(est, panel)
se
```


```{r, fig.retina=2}
plot(est, se)
```
