---
title: "Preprocessing CHC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preprocessing CHC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load raw Community Health Centers dataset
```{r setup}
data("CHC_original", package = "seq.sdid")
```

## Create treatment indicator column
```{r}
chc_df["year"] <- format(chc_df$year, format = "%Y")
# Assign adoption year to never-treated; The latest adoption year is 1980
chc_df$chc_year_exp[is.na(chc_df$chc_year_exp)] <- 2500
chc_df$W <- as.numeric(chc_df$chc_year_exp <= chc_df$year)
```

## Remove 3 most populous counties
```{r}
chc_df <- chc_df[(chc_df$stfips != 36) | (chc_df$cofips != 61), ]
chc_df <- chc_df[(chc_df$stfips != 6) | (chc_df$cofips != 37), ]
chc_df <- chc_df[(chc_df$stfips != 17) | (chc_df$cofips != 31), ]
```

## Drop rows having NA in either treatment indicator column or age-adjusted mortality rate
```{r}
chc_df <- chc_df[!is.na(chc_df$W) & !is.na(chc_df$amr), ]
```

## Create covariate with 5 distinct values based on share of urban dwellers in the county in 1960
```{r}
chc_df$Durb <- 25*round(chc_df$`_60pcturban` / 25)
colnames(chc_df)[5] <- "adoption_date"
```

## Remove observations post-1988 to match the original research, which covered the period from 1959 to 1988
```{r}
chc_df$Durb <- factor(chc_df$Durb)
chc_df <- chc_df[chc_df$year <= 1988, ]
```

## Save the preprocessed dataframe
```{r}
df_final <- subset(chc_df, select=c(fips, amr, year, W, Durb, popwt))
colnames(df_final) <- c("county", "mort", "year", "CHC", "urb_share", "popwt")
write.csv(df_final, "CHC.csv", row.names = FALSE)
```
